### 2019-08-10 results.tex
Remove aTGC
General touching up

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_weng_phoPt.pdf}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_wmng_phoPt.pdf}
    \caption{
      Postfit reconstructed \ETgamma\ distribution in the two control regions used in the cross section likelihood function:
      \Pe\Pgamma\ (left) and \Pmu\Pgamma\ (right). The last bin includes all events with $\ETgamma > 1000\unit{GeV}$.
    }
    \label{fig:postfitXS_CR}
  \end{center}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_znng_SA_phoPt.pdf}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_znng_SB_phoPt.pdf}
    \caption{
      Postfit reconstructed \ETgamma\ distribution in the two signal regions used in the cross section likelihood function:
      vertical (left) and horizontal (right). The last bin includes all events with $\ETgamma > 1000\unit{GeV}$.
    }
    \label{fig:postfitXS_SR}
  \end{center}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_unfolding_b_phoPt.pdf}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_unfolding_b_genPtAllocation_phoPt.pdf}
    \caption{
      Sum of the postfit reconstructed \ETgamma\ distributions of the two signal regions used in the cross section likelihood function.
      On the left, the separate background contributions are assigned different colors, while \zinvg\ contributions from every bin of true
      \pTgamma\ are assigned the same green color. On the right, all background contributions are assigned the same gray color, while
      contributions from separate \pTgamma\ bins are assigned different colors. The last \ETgamma\ bin includes all events
      with $\ETgamma > 1000\unit{GeV}$.
    }
    \label{fig:postfitXS_combSR}
  \end{center}
\end{figure}

@@

The theoretical SM prediction, as computed in MATRIX to NNLO in $\alpha_\mathrm{S}$, is listed for each true \pTgamma\ bin in Table~\ref{tab:matrix_xsec}, which
also lists the uncertainties on the prediction due to the choice of renormalization and factorization scales (scale uncertainty). The MATRIX predictions
and the measurement reported above generally agree to within the statistical errors of the measurement, except in the highest \pTgamma\ bins: the difference
between the measured and predicted cross section in the 400-600\unit{GeV} bin is 1.6 times the statistical error on the measurement, and the difference
for the 600-Inf bin is 1.8 times the statistical error. The \zinvg\ process contributes an estimated 14.12 events to the observed 16 events in the 600-Inf bin.
Under the hypothesis that the MATRIX prediction is true, the probability of observing at least 14 \zinvg\ events
from the 600-Inf bin is about 1\%\footnote{Assuming that these events are produced via a Poisson process with mean
$\sigma_\mathrm{MATRIX}*L = 19.71$ and that each produced event is observed with probability 0.3508 (estimated in MC).}.
This falls far short of the standard ``$5\sigma$'' (about 0.00003\%) criterion for rejecting the SM and claiming discovery of new physics, in particular
since the look-elsewhere effect~\cite{ref:08-AOAS163} is not being accounted for and also since no specific BSM model is being compared here.
However, it does indicate a notable tension with the MATRIX NNLO predictions that should be kept in mind in future studies.

@@

\section{aTGC limits} \label{sec:results_aTGC}
\section{DM simplified model limits} \label{sec:results_DM}
Figure~\ref{fig:postfitDM_CR} shows the postfit plots in the control regions corresponding to the DM and ADD likelihood function (with
BSM signal strength fixed to zero\footnote{For nonzero values of the BSM signal strength, the plots depend on a specific choice of BSM model
and parameters. Fixing the signal strength to zero gives a ``model-independent'' perspective on the SM backgrounds,
and essentially illustrates what the estimated backgrounds look like if BSM physics makes imperceptibly
small contributions to observed event yields.}).
Figure~\ref{fig:postfitDM_SR} shows the postfit background distributions in the vertical and horizontal signal regions.
Figure~\ref{fig:2d_mm} shows $\mu_{95}$ in the \mmed--\mdm\ plane for the  vector and
axial-vector mediator scenarios, based on the NLO DM simplified model samples. The solid red curves are the
contours of expected $\mu_{95} = 1$. The DM simplified model hypothesis is excluded at 95\% CL or above in the region with $\mu_{95} < 1$.
For both vector and axial-vector mediators, mediator masses of up to 950\unit{GeV} (observed), 1150\unit{GeV} (expected) are excluded
for small \mdm\ values.
% Figure~\ref{fig:pullsDM} shows how various nuisance parameters are constrained and shifted as
% a result of the fit. None of the parameters are significantly constrained or shifted by the fit.
% Figure~\ref{fig:impacts1} shows
% the impacts of various nuisances parameters on the 95\% CL upper limit of the BSM signal strength for the DM simplified model,
% with a vector mediator of mass $\mmed = 1000\unit{GeV}$ and a dark matter particle of mass $\mdm = 1\unit{GeV}$.

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_005-a.pdf}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_005-b.pdf}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_005-c.pdf}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_005-d.pdf}
    \caption{
      Postfit \ETgamma\ distribution in each of the four control regions used in the DM and ADD likelihood function:
      \Pe\Pe\Pgamma\ (top left), \Pmu\Pmu\Pgamma\ (top right), \Pe\Pgamma\ (bottom left), and
      \Pmu\Pgamma\ (bottom right). The last bin includes all events with $\ETgamma > 1000\unit{GeV}$.
      Published in~\cite{ref:JHEP02(2019)074}.
    }
    \label{fig:postfitDM_CR}
  \end{center}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_006-b.pdf}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_006-a.pdf}
    \caption{
      Postfit \ETgamma\ distributions in the vertical (left) and horizontal (right) signal regions, corresponding
      to the DM and ADD likelihood function with BSM signal strength set to zero.
      The last bin includes all events with $\ETgamma > 1000\unit{GeV}$.
      Published in~\cite{ref:JHEP02(2019)074}.
    }
    \label{fig:postfitDM_SR}
  \end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.48\linewidth]{figures/exo16053/Figure_008-a.pdf}
    \includegraphics[width=0.48\linewidth]{figures/exo16053/Figure_008-b.pdf}
    \caption{
      The 90\% CL exclusion limits on the DM--nucleon spin-independent (left)
      and spin-dependent (right) scattering cross sections involving vector and axial-vector mediators, respectively,
      as a function of \mdm. Simplified model parameters of $\gq=0.25$ and $\gdm=1$ are assumed.
      The region to the upper left of the contour is excluded at 95\% CL or above. At the scale of these plots, the median
      expected 90\% CL curves largely overlap the observed 90\% CL curves.
      Published in~\cite{ref:JHEP02(2019)074}.
    }
    \label{fig:2d_mx}
  \end{center}
\end{figure}

@@

\begin{table}[htbp]
  \begin{center}
    \caption{The 95\% CL observed and expected lower limits on the ADD mass scale \mD\ as a function of $n$, the number of extra dimensions.}
    \label{tab:MDLimits}
    \begin{tabular}{|c|c|c|}
      \hline
      $n$ & Obs. limit [TeV] & Exp. limit [TeV] \\
      \hline
      3 & 2.85 & 3.32 \\
      4 & 2.86 & 3.29 \\
      5 & 2.88 & 3.28\\
      6 & 2.90 & 3.28 \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

>>>>

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_weng_phoPt.pdf}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_wmng_phoPt.pdf}
    \caption{
      Control region postfit \ETgamma\ distributions corresponding to the cross section likelihood function:
      \Pe\Pgamma\ (left) and \Pmu\Pgamma\ (right). The last bin includes all events with $\ETgamma > 1000\unit{GeV}$.
    }
    \label{fig:postfitXS_CR}
  \end{center}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_znng_SA_phoPt.pdf}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_znng_SB_phoPt.pdf}
    \caption{
      Signal region postfit \ETgamma\ distributions corresponding to the cross section likelihood function:
      vertical region (left) and horizontal region (right).
      The last bin includes all events with $\ETgamma > 1000\unit{GeV}$.
    }
    \label{fig:postfitXS_SR}
  \end{center}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_unfolding_b_phoPt.pdf}
    \includegraphics[width=0.45\textwidth]{figures/xsec_results/Postfit/postfit_unfolding_b_genPtAllocation_phoPt.pdf}
    \caption{
      Sum of the postfit reconstructed \ETgamma\ distributions of the two signal regions corresponding to the cross section likelihood function.
      On the left, the separate background contributions are assigned different colors, while \zinvg\ contributions from every bin of true
      \pTgamma\ are assigned the same green color. On the right, all background contributions are assigned the same gray color, while
      contributions from separate \pTgamma\ bins are assigned different colors. The last \ETgamma\ bin includes all events
      with $\ETgamma > 1000\unit{GeV}$.
    }
    \label{fig:postfitXS_combSR}
  \end{center}
\end{figure}

@@

The theoretical SM prediction, as computed in MATRIX to NNLO in $\alpha_\mathrm{S}$, is listed for each true \pTgamma\ bin in Table~\ref{tab:matrix_xsec}, which
also lists the uncertainties on the prediction due to the choice of renormalization and factorization scales (scale uncertainty). Figure~\ref{fig:measvsmat}
compares the measured cross section to the MATRIX predictions.
The two generally agree to within the statistical errors of the measurement, except in the highest \pTgamma\ bins: the difference
between the measured and predicted cross section in the 400-600\unit{GeV} bin is 1.6 times the statistical error on the measurement, and the difference
for the 600-Inf bin is 1.8 times the statistical error. The \zinvg\ process contributes an estimated 14.12 events to the observed 16 events in the 600-Inf bin.
Under the hypothesis that the MATRIX prediction is true, the probability of observing at least 14 \zinvg\ events
from the 600-Inf bin is about 1\%\footnote{Assuming that these events are produced via a Poisson process with mean
$\sigma_\mathrm{MATRIX}*L = 19.71$ and that each produced event is observed with probability 0.3508 (estimated in MC).}.
This falls far short of the standard ``$5\sigma$'' (about 0.00003\%) criterion for rejecting the SM and claiming discovery of new physics, in particular
since the look-elsewhere effect~\cite{ref:08-AOAS163} is not being accounted for and also since no specific BSM model is being compared here.
However, it does indicate a notable tension with the MATRIX NNLO predictions that should be kept in mind in future studies.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.75\textwidth]{figures/ZNuNuG_measured_vs_MATRIX.pdf}
    \caption{
      The measured \zinvg\ cross section (blue) compared to the MATRIX NNLO prediction (red). The vertical bars and hatched bands
      on the measured cross section correspond to the statistical and systematic uncertainties, respectively. The scale uncertainty
      on the MATRIX cross section is too small to be seen on this plot. The last bin includes all events with $\pTgamma > 1000\unit{GeV}$.
    }
    \label{fig:measvsmat}
  \end{center}
\end{figure}

\section{DM simplified model limits} \label{sec:results_DM}
Figure~\ref{fig:postfitDM_CR} shows the postfit plots in the control regions corresponding to the DM and ADD likelihood function (with
BSM signal strength fixed to zero\footnote{For nonzero values of the BSM signal strength, the plots depend on a specific choice of BSM model
and parameters. Fixing the signal strength to zero gives a ``model-independent'' perspective on the SM backgrounds,
and essentially illustrates what the estimated backgrounds look like if BSM physics makes imperceptibly
small contributions to observed event yields.}).
Figure~\ref{fig:postfitDM_SR} shows the postfit background distributions in the vertical and horizontal signal regions.
Figure~\ref{fig:2d_mm} shows $\mu_{95}$ in the \mmed--\mdm\ plane for the  vector and
axial-vector mediator scenarios, based on the NLO DM simplified model samples. The solid red curves are the
contours of expected $\mu_{95} = 1$. The DM simplified model hypothesis is excluded at 95\% CL or above in the region with $\mu_{95} < 1$.
For both vector and axial-vector mediators, mediator masses of up to 950\unit{GeV} (observed), 1150\unit{GeV} (expected) are excluded
for small \mdm\ values.
% Figure~\ref{fig:pullsDM} shows how various nuisance parameters are constrained and shifted as
% a result of the fit. None of the parameters are significantly constrained or shifted by the fit.
% Figure~\ref{fig:impacts1} shows
% the impacts of various nuisances parameters on the 95\% CL upper limit of the BSM signal strength for the DM simplified model,
% with a vector mediator of mass $\mmed = 1000\unit{GeV}$ and a dark matter particle of mass $\mdm = 1\unit{GeV}$.

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_005-a.pdf}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_005-b.pdf}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_005-c.pdf}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_005-d.pdf}
    \caption{
      Control region postfit \ETgamma\ distribution corresponding to the DM and ADD likelihood function:
      \Pe\Pe\Pgamma\ (top left), \Pmu\Pmu\Pgamma\ (top right), \Pe\Pgamma\ (bottom left), and
      \Pmu\Pgamma\ (bottom right). The last bin includes all events with $\ETgamma > 1000\unit{GeV}$.
      Published in~\cite{ref:JHEP02(2019)074}.
    }
    \label{fig:postfitDM_CR}
  \end{center}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_006-b.pdf}
    \includegraphics[width=0.45\textwidth]{figures/exo16053/Figure_006-a.pdf}
    \caption{
      Signal region postfit \ETgamma\ distributions corresponding to the DM and ADD likelihood function, with
      BSM signal strength set to zero: vertical region (left) and horizontal region (right). The last bin includes all events with $\ETgamma > 1000\unit{GeV}$.
      Published in~\cite{ref:JHEP02(2019)074}.
    }
    \label{fig:postfitDM_SR}
  \end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.48\linewidth]{figures/exo16053/Figure_008-a.pdf}
    \includegraphics[width=0.48\linewidth]{figures/exo16053/Figure_008-b.pdf}
    \caption{
      The 90\% CL exclusion limits on the DM--nucleon spin-independent (left)
      and spin-dependent (right) scattering cross sections involving vector and axial-vector mediators, respectively,
      as a function of \mdm. Simplified model parameters of $\gq=0.25$ and $\gdm=1$ are assumed.
      The region to the upper left of the contour is excluded at 95\% CL or above. Published in~\cite{ref:JHEP02(2019)074}.
    }
    \label{fig:2d_mx}
  \end{center}
\end{figure}

@@

\begin{table}[htbp]
  \begin{center}
    \label{tab:MDLimits}
    \begin{tabular}{|c|c|c|}
      \hline
      $n$ & Obs. limit [TeV] & Exp. limit [TeV] \\
      \hline
      3 & 2.85 & 3.32 \\
      4 & 2.86 & 3.29 \\
      5 & 2.88 & 3.28\\
      6 & 2.90 & 3.28 \\
      \hline
    \end{tabular}
    \caption{The 95\% CL observed and expected lower limits on the ADD mass scale \mD\ as a function of $n$, the number of extra dimensions.}
  \end{center}
\end{table}
